%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%
\begin{document}

%----------HEADING(SPACEBTWN)----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://kenf.dev/}{\Large Kenneth Gao}} & Email : \href{mailto:kenneth.gwb@gmail.com}{kenneth.gwb@gmail.com}\\
%   \href{http://kenf.dev/}{http://kenf.dev} & +65 8884 4154 \\
% \end{tabular*}

%----------HEADING(CENTER)----------
\begin{center}
    \textbf{\Huge \scshape Kenneth Gao} \\ \vspace{1pt}
    \small +65 8884 4154 $|$ \href{mailto:kenneth.gwb@gmail.com}{\underline{kenneth.gwb@gmail.com}} $|$ 
    \href{https://linkedin.com/in/thisiskenf/}{\underline{linkedin.com/in/thisiskenf}} $|$
    \href{https://github.com/duckyfuz/}{\underline{github.com/duckyfuz}}
\end{center}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Software Engineering Intern}{Jan. 2024 -- Present}
      {NodeFlair - Tech Career Platform for Southeast Asia}{Singapore}
      \resumeItemListStart
      \resumeItem{NodeFlair is a startup that connects tech talents with job opportunities, streamlining the recruitment process}
        \resumeItem{Enhanced functionality of the existing API for new services on the Ruby on Rails backend}
        \resumeItem{Utilized A/B testing methodology to optimize user experience, resulting in a 15\% increase in click-through rate}
        \resumeItem{Created an internal UI library in React to ensure design consistency across site}
      \resumeItemListEnd
    \resumeSubheading
      {Programming Lead}{Nov. 2023 -- Present}
      {CloudHacks 2024}{Singapore}
      \resumeItemListStart
        \resumeItem{Led a team of 3 using Agile methodology to redesign and rebuild promotional website with the Nextjs framework}
      \resumeItemListEnd
    \resumeSubheading
      {Software Engineering / Machine Learning Intern}{Nov. 2023 -- Jan. 2024}
      {xDATA, Home Team Science and Technology Agency (HTX)}{Singapore}
      \resumeItemListStart
        \resumeItem{Worked on Vertext, an in-house NLP tool serving 10+ government agencies - redesigned frontend with React to improve UX and refactored codebase to reuse components for cleaner implementation}
        \resumeItem{Constructed knowledge graphs from unstructured text with GenAI to enhance multi-hop question answering (QA) performance during retrieval augmented generation (RAG), leading to greater context precision}
    \resumeItemListEnd
    \resumeSubheading
      {SSP Platoon Commander}{Dec. 2022 -- Nov. 2023}
      {16C4I Bn, Singapore Armed Forces}{Singapore}
      \resumeItemListStart
        \resumeItem{Led a 20+ member platoon to maintain constant battalion operational readiness}
        \resumeItem{Automated administrative chores such as duty scheduling via scripting, leading to time savings of over 60\%}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {National University of Singapore}{Singapore}
      {Bachelor of Engineering in Computer Engineering, E-Scholars Programme (3yrs BEng + 1yr MSc)}{}
    \resumeSubheading
      {Hwa Chong Institution}{Singapore}
      {GCE A-Levels, 90RP (PCME) with H3 Physics Distinction}{}
\resumeSubHeadingListEnd

%-----------AWARDS-----------
\section{Awards}
\resumeSubHeadingListStart
  \resumeProjectHeading
      {\textbf{HTX's HacX!} $|$ \emph{2nd Runner-up}}{Nov. 2023}
      \resumeItemListStart
        \resumeItem{Developed an application that utilises VGG16 and YOLOv8 to accelerate the tool accounting process for contractors entering secure facilities}
      \resumeItemListEnd
  \resumeProjectHeading
      {\textbf{SCS’s Splash Awards} $|$ \emph{1st Place}}{Oct. 2023}
      \resumeItemListStart
        \resumeItem{Developed a full-stack native application featuring a gamified way to learn about Singapore’s culture}
      \resumeItemListEnd
  \resumeProjectHeading
      {\textbf{SUTD's What the Hack} $|$ \emph{1st Place}}{Aug. 2023}
      \resumeItemListStart
        \resumeItem{Developed an emotion-recognition application leveraging upon LLMs}
      \resumeItemListEnd
  \resumeProjectHeading
      {\textbf{CloudHacks} $|$ \emph{1st Place}}{Aug. 2023}
      \resumeItemListStart
        \resumeItem{Developed an articles-to-podcast application for personalised news consumption}
      \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart
  \resumeProjectHeading
      {\textbf{\href{https://kenf.hashnode.dev/treehouse}{\underline{treehouse}}} $|$ Full-stack web application for sharing community-wide activites, built with React and AWS}{}
  \resumeProjectHeading
      {\textbf{\href{https://github.com/duckyfuz/expense_tracker}{\underline{Budgety}}} $|$ Full-stack native application for tracking expenses and viewing insights, built with React Native and Firebase}{}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: JavaScript, Python, Ruby, C/C++, SQL, PostgreSQL, HTML/CSS} \\
     \textbf{Frameworks}{: React, React Native, Node.js, Flask, Django} \\
     \textbf{Developer Tools}{: Git, Docker, AWS, Microsoft Azure, Google Cloud Platform, Firebase} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib, TensorFlow, PyTorch, LangChain}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
